Brief Announcement: An Improved Lower Bound for Dynamic Graph Partitioning

### 2020-01-22 paper/paper.tex
Minor rewrite of intro
Comments
More comments

\maciek{$. \rightarrow \cdot$}
\maciek{Font for OPT, ALG, DET, dist etc}

Let $P_I = I_1, \dots, I_{\ell}$ denote the initial partition with which both ON and OPT begin and
$P_F = F_1, \dots, F_{\ell}$ the final partition.
\begin{definition}	\label{def:dist}
    The \emph{distance} of a partition $P = C_1, \dots, C_{\ell}$ is the number of nodes in $P$ that do not reside in their initial cluster.
    That is,
    $dist(P, P_I) = \sum_{j=1}^{\ell} | C_j \setminus I_j |$. 
\end{definition}

@@

@@

    \begin{theorem}
      There exists a $O(\ell)$-competitive algorithm for $k=3$.
    \mahmoud{is this needed anymore?}
    \end{theorem}

>>>>

Let $P_I = I_1, \dots, I_{\ell}$ denote the initial partition with which both ON and OPT begin and
$P_F = F_1, \dots, F_{\ell}$ the final partition.
\begin{definition}	\label{def:dist}
    The \emph{distance} of a partition $P = C_1, \dots, C_{\ell}$ is the number of nodes in $P$ that do not reside in their initial cluster.
    That is,
    $dist(P, P_I) = \sum_{j=1}^{\ell} | C_j \setminus I_j |$. 
\end{definition}
\maciek{We should figure out a better name than "distance". We usually apply two arguments to distance. Examples of names that can be applied to only one configuration as a parameter: radius, span, stretch, spread, width. Also: difference, disparity, distinction, alternation}

@@

\todo{$. \rightarrow \cdot$}

\todo{Font for OPT, ALG, DET, dist etc}

@@

    \begin{theorem}
      There exists a $O(\ell)$-competitive algorithm for $k=3$.
    \mahmoud{is this needed anymore?}
    \maciek{It does not overlap with any other result from this paper.}
    \end{theorem}
